### 2016-07-31 doc/publications/plos16/plos16.tex
plos16.tex

@@

>>>>

Cursed Forest uses:
\begin{itemize}
\item an ``information gained'' criteria for splitting.
\item variabel importance is the sum of IG over all notes and all trees for that variable
\item the model of parallelism is different to the ``foreach'' method -- we need to describe it
\end{itemize}

@@

\marginpar{These are regression examples, we nned some classification examples}
